\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-08-30 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS_10pg.tex
updates

Fig. \ref{fig:CompTimeIEEE14bus} shows the computational times for updating $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ via the algorithm in Sec. \ref{sec:ProxAlgo} for \textbf{Cases I} and \textbf{II}.

>>>>

Fig. \ref{fig:CompTimeIEEE14bus} shows the computational times for updating the point clouds $\{\bm{x}_{k}^{i},\varrho_{k}^{i}\}_{i=1}^{N}$ via the algorithm in Sec. \ref{sec:ProxAlgo} for \textbf{Cases I} and \textbf{II}.
